`r glue::glue('inferCNV results for {params$library_id} with {params$reference_name} reference')`

### 2025-05-14 analyses/infercnv-consensus-cell-type/template-notebooks/SCPCP000015_explore-infercnv-results.Rmd
update param and text handling for _pooled/internal

---
title: "`r glue::glue('inferCNV results for {params$library_id} with {params$reference_name} reference')`"
author: "Stephanie J. Spielman"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_depth: 3
    code_folding: hide
params:
  library_id: SCPCL000822
  sample_id: SCPCS000490
  reference_name: ref_endo
---

@@

```{r, results = 'asis'}
ref_text <- list(
  "ref_endo" = "endothelial",
  "ref_immune" = "immune",
  "ref_endo-immune" = "endothelial and immune"
)
if (stringr::str_detect(opts$reference_name, "internal")) {
  reference_type_text <- glue::glue("within the `SCPCL000822` library")
} else {
  reference_type_text <- glue::glue("across all `SCPCP000015` libraries")
}

glue::glue(
  "`inferCNV` was run with the following normal reference: `{params$reference_name}`.
  This reference contains all {ref_text[[params$reference_name]]} cells {reference_type_text}, excluding any which were also identified as tumor in the `cell-type-ewings` analysis module.
  "
)
```

>>>>

---
title: "`r glue::glue('inferCNV results for {params$library_id} with {params$reference_name} reference')`"
author: "Stephanie J. Spielman"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_depth: 3
    code_folding: hide
params:
  library_id: SCPCL000822
  sample_id: SCPCS000490
  reference_name: endo_pooled
---

@@

```{r, results = 'asis'}
ref_celltype <- stringr::str_split(params$reference_name, "_")[1]
ref_type <- stringr::str_split(params$reference_name, "_")[2]

ref_text <- list(
  "endo" = "endothelial",
  "immune" = "immune",
  "endo-immune" = "endothelial and immune"
)
if (ref_type == "internal") {
  reference_type_text <- glue::glue("within the {params$library_id} library")
} else {
  reference_type_text <- glue::glue("across all `SCPCP000015` libraries")
}

glue::glue(
  "`inferCNV` was run with the following normal reference: `{params$reference_name}`.
  This reference contains all {ref_celltype} cells {reference_type_text}, excluding any which were also identified as tumor in the `cell-type-ewings` analysis module.
  "
)
```
